### 2013-06-06 inst/examples/semi-analytic-posteriors.Rmd

```{r plotting-options, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE}
source("~/.knitr_defaults.R")
require(reshape2)
require(data.table)
opts_chunk$set(warning=TRUE, message=TRUE, cache=FALSE)
#opts_knit$set(upload.fun = socialR::flickr.url)
```

>>>>

```{r plotting-options, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE}
source("~/.knitr_defaults.R")
require(reshape2)
require(data.table)
opts_chunk$set(warning=TRUE, message=TRUE, cache=FALSE)
opts_knit$set(upload.fun = socialR::flickr.url)
```
